A Paucity of Young Stars and Planets in the Kepler Field

### 2024-06-05 paper/ms.tex
update ms

\subsection{A Dearth Of Young Stars And Planets}

The stellar ages are given in Table~\ref{tab:planets} for the known
planet hosts, and in Table~\ref{tab:stars} for all Kepler stars.
Figure~\ref{fig:hist_tgyro} shows the rotation-based age distributions
of all the stars (left column) and the KOI hosts (middle column).
These ``histograms'' are sampled from the posterior probability
distributions by drawing ten random samples from each posterior, and
then computing the re-weighted histogram of the resulting samples.
The uncertainties assume Poisson statistics.  We truncated the plots
near $4$\,Gyr since this is the cluster age out to which our
interpolation-based method is well-calibrated.  The overall slope
yields a dearth of young stars relative to the expectation of a
uniform age distribution.
%In an alternative coinage, this tendency for fewer young
%stars to be present could also be dubbed a ``demographic cliff'',
%in reference to the phenomenon from human demography.

@@

Let us focus discussion on blemish-free stars with 
blemish-free planets: $Q_{\rm star}$ must not have any of bits zero
through nine raised, and $Q_{\rm planet}$ must similarly have no quality flags
raised.  Under this constraint, our results include
\ltonegyrhighqconfirmedtwosided\ confirmed planets younger than 1\,Gyr with
two-sided $t_{\rm gyro}$ and $t_{\rm Li}$, and
\ltonegyrhighqconfirmedonesided\ confirmed planets with comparable
ages for which $t_{\rm gyro}$
provides an age constraint while $t_{\rm Li}$ is one-sided.

Figure~\ref{fig:rp_period_age_results} shows
the planets and planet candidates with $t_{\rm gyro}$$<$1\,Gyr at
2$\sigma$.  
This figure includes \nconfirmedplyounggyrotwosigmanograzingnoruwe\
confirmed Kepler planets, and
\ncandidateplyounggyrotwosigmanograzingnoruwe\ candidate planets, all of which
are listed in Table~\ref{tab:planets}.
These include
\nearthshighqconfirmed\ Earth-sized or smaller planets,
one Jovian planet candidate, \nsubsaturnshighqconfirmed\
``super-Neptune'' ($>$4\,$R_\oplus$) sized planets,
\nminineptuneshighqconfirmed\ mini-Neptunes above the radius valley
as parametrized by \citealt{2018MNRAS.479.4786V}, and
\nsuperearthshighqconfirmed\ super-Earth sized planets below the
radius valley.  While most of these planets are on orbital periods
below 50\,days, \nlongperiodhighqconfirmed\ are on more distant
orbits.

A few highlights from these systems include
Kepler-1529, Kepler-1565, Kepler-1312, and Kepler-1629.  Kepler-1529b
is a $\approx$100$\pm$50\,Myr mini-Neptune with well-measured rotation
and lithium ages.  Kepler-1565b is an analogous $\approx$170-230\,Myr
super-Earth.  Kepler-1312 is a $t_{\rm gyro}$=\kepthirteentwelve\,Myr
near-Solar analog with an Earth-sized planet
on a one-day orbit, and a mini-Neptune on a five-day orbit.  The
Earth-sized planet, Kepler-1312~c, along with the near-identical
Kepler-1561~b ($t_{\rm gyro}$=\kepfifteensixone\,Myr), rank among the
youngest Earth-sized planets currently known, comparable to systems
such as HD~63433d \citep[1.1\,$R_\oplus$,
$414$$\pm$$23$\,Myr;][]{2024AJ....167...54C} and TOI-1807~b
\citep[1.3\,$R_\oplus$, 180$\pm$40\,Myr;][]{2021AJ....162...54H}.
Kepler-1629~b, with a size just two-thirds that of Earth
(0.67$\pm$0.05\,$R_\oplus$), is marginally older, also based on
rotation (\kepsixteentwonine\,Myr).  The lithium age from a
reconnaissance TRES spectrum confirms the point.

>>>>

\subsection{A Paucity Of Young Stars And Planets}

The stellar ages are given in Table~\ref{tab:planets} for the known
planet hosts, and in Table~\ref{tab:stars} for all Kepler stars.
Figure~\ref{fig:hist_tgyro} shows the rotation-based age distributions
of all the stars (left column) and the KOI hosts (middle column).
These ``histograms'' are sampled from the posterior probability
distributions by drawing ten random samples from each posterior, and
then computing the re-weighted histogram of the resulting samples.
The uncertainties assume Poisson statistics.  We truncated the plots
near $4$\,Gyr since this is the cluster age out to which our
interpolation-based method is well-calibrated.  The overall slope
yields a paucity of young stars relative to the expectation of a
uniform age distribution.
%In an alternative coinage, this tendency for fewer young
%stars to be present could also be dubbed a ``demographic cliff'',
%in reference to the phenomenon from human demography.

@@

Let us focus on blemish-free stars with 
blemish-free planets: $Q_{\rm star}$ must not have any of bits zero
through nine raised, and $Q_{\rm planet}$ must similarly have no quality flags
raised.  Under this constraint, our results include
\ltonegyrhighqconfirmedtwosided\ confirmed planets younger than 1\,Gyr with
two-sided $t_{\rm gyro}$ and $t_{\rm Li}$, and
\ltonegyrhighqconfirmedonesided\ confirmed planets with comparable
ages for which $t_{\rm gyro}$
is two-sided while $t_{\rm Li}$ is one-sided.

Figure~\ref{fig:rp_period_age_results} shows
the planets and planet candidates with $t_{\rm gyro}$$<$1\,Gyr at
2$\sigma$.  
This figure includes \nconfirmedplyounggyrotwosigmanograzingnoruwe\
confirmed Kepler planets, and
\ncandidateplyounggyrotwosigmanograzingnoruwe\ candidate planets, all of which
are listed in Table~\ref{tab:planets}.
These include
\nearthshighq\ objects Earth-sized or smaller,
\njupitershighq\ Jovian-sized planet candidates, \nsubsaturnshighq\
super-Neptunes (4--10\,$R_\oplus$),
\nminineptuneshighq\ mini-Neptunes above the radius valley
as parametrized by \citealt{2018MNRAS.479.4786V}, and
\nsuperearthshighq\ super-Earth sized planets below the
radius valley.  While most of these planets are on orbital periods
below 50\,days, \nlongperiodhighq\ are on more distant
orbits.

Highlights from these systems include
Kepler-1529, Kepler-1565, Kepler-1312, and Kepler-1629.  Kepler-1529b
is a $\approx$100$\pm$50\,Myr mini-Neptune with well-measured rotation
and lithium ages.  Kepler-1565b is an analogous $\approx$170-230\,Myr
super-Earth.  Kepler-1312 is a $t_{\rm gyro}$=\kepthirteentwelve\,Myr
near-Solar analog with an Earth-sized planet
on a one-day orbit, and a mini-Neptune on a five-day orbit.  The
Earth-sized planet, Kepler-1312~c, along with the near-identical
Kepler-1561~b ($t_{\rm gyro}$=\kepfifteensixone\,Myr), rank among the
youngest Earth-sized planets currently known, comparable to planets
such as HD~63433d \citep[1.1\,$R_\oplus$,
$414$$\pm$$23$\,Myr;][]{2024AJ....167...54C} and TOI-1807~b
\citep[1.3\,$R_\oplus$, 180$\pm$40\,Myr;][]{2021AJ....162...54H}.
Kepler-1629~b, with a size just two-thirds that of Earth
(0.67$\pm$0.05\,$R_\oplus$), is marginally older, also based on
rotation (\kepsixteentwonine\,Myr).  The lithium age from a
reconnaissance TRES spectrum confirms the point.
